weather_2

### 2021-08-28 data analysis/weather/weather_2.Rmd
as

---
title: "weather"
author: "Maxwel Coura Oliveira"
date: "7/8/2021"
output: html_document
---

```{r}
library(tidyverse) # Data wrangling
library(lubridate) # Dates operations
library(daymetr)
library(chirps)
library(patchwork)
library(ggtext)
library(nasapower)
library(vegan)
```

@@

```{r}
adaptation_weather1 %>% 
  ggplot(aes(x = month_lab, y = tmean)) +
  geom_jitter(aes(color = variable), alpha = 0.05, shape = 0) +
  scale_color_manual(values = c("red", "blue", "gray90")) +
  facet_grid(~ site) +
  geom_line(adaptation_weather1 %>% 
               filter(year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "red") +
  geom_line(adaptation_weather1 %>% 
               filter(year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean, group = 1), 
             color = "blue") +
  geom_point(adaptation_weather1 %>% 
               filter(year %in% c(2018)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "red", shape = 22, size = 3) +
  geom_point(adaptation_weather1 %>% 
               filter(year %in% c(2019)) %>% 
               group_by(site, month_lab) %>% 
               summarise(tmean = mean(tmean)),
             mapping = aes(x = month_lab, y = tmean), 
             fill = "blue", shape = 22, size = 3) +
  geom_richtext(data = text1, aes(x = 2, y = 7), lineheight = 0.4, 
            label = "Mean air temperature <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 6, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text2, aes(x = 2.2, y = 10), lineheight = 0.4, 
            label = "30 years <br>daily mean <br>air temperature", size = 6, 
             label.color = NA, fill = NA, color = "gray90") +
  geom_curve(data = text2, 
             x = 2, y = 13, 
             xend = 2.5, yend = 16,
             arrow = arrow(length = unit(0.07, "inch")), 
             size = 0.4, curvature = -0.3, color = "gray90") + 
  scale_y_continuous(limits = c(0, 32)) +
  labs(x = NULL, y = "Temperature (C)") +
  theme_test() +
  theme(legend.position = "none",
#        strip.text = element_markdown(size = 15, hjust = 0.5),
#        axis.text.y = element_markdown(size = 25),
#        axis.title = element_markdown(size = 27),
#        axis.text.x = element_markdown(size = 25)#,
#        legend.text = element_markdown(size = 25)
        )  -> temp

ggsave("weather.png", height = 3, width = 6)
```

>>>>

---
title: "weather_2"
author: "Maxwel Coura Oliveira"
date: "8/28/2021"
output: html_document
---

```{r}
library(tidyverse) # Data wrangling
library(lubridate) # Dates operations
library(daymetr)
library(chirps)
library(patchwork)
library(ggtext)
library(nasapower)
library(ggdist)
library(vegan)
```

@@

```{r}
adaptation_weather1 %>% 
  filter(variable != "NA") %>% 
  ggplot(aes(x = month_lab, y = tmean, fill = variable)) +
  geom_jitter(data = adaptation_weather1 %>% 
                filter(variable == "NA"), show.legend = FALSE, 
              color = "#333333", alpha = 0.02, shape = 16) +
#   geom_jitter(position = position_dodge2(width = 0.4),
#              color = "#333333", alpha = 1, shape = 16) +
  stat_gradientinterval(position ="dodge") +
  scale_fill_manual(values = c("red", "blue", "#333333")) +
  facet_grid(~ site) +
  theme_test() +
  geom_richtext(data = text1, aes(x = 2, y = 7), lineheight = 0.4, 
            label = "Mean air temperature <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 2, 
            label.color = NA, fill = NA) +
  geom_richtext(data = text2, aes(x = 2.2, y = 10), lineheight = 0.4, 
            label = "30 years <br>daily mean <br>air temperature", size = 2, 
             label.color = NA, fill = NA, color = "gray90") +
#  geom_curve(data = text2, 
#             x = 2, y = 13, 
#             xend = 2.5, yend = 16,
#             arrow = arrow(length = unit(0.07, "inch")), 
#             size = 0.4, curvature = -0.3, color = "gray90") + 
  scale_y_continuous(limits = c(0, 33)) +
  labs(x = NULL, y = "Temperature (C)") +
  theme(legend.position = "none") -> temp

ggsave("weather.png", height = 3, width = 9)
```
